The Freeplay Sandbox: a Novel Methodology for the Evaluation of Social Robotics

### 2017-10-06 paper.tex
Line wrappping

Capturing all the interactions taking place during the play sessions is possible
and practical with this setup. Even though the children will typically move a
little, the task is fundamentally a face-to-face, spatially delimited,
interaction, and as such simplifies the data collection. For instance, during
our dataset acquisition campaign (120 children, more than 45h of footage), the
children's faces were automatically detected in 97\% \textcolor{red}{[TODO: check that!]} of the
recorded frames.

>>>>

Capturing all the interactions taking place during the play sessions is possible
and practical with this setup. Even though the children will typically move a
little, the task is fundamentally a face-to-face, spatially delimited,
interaction, and as such simplifies the data collection. For instance, during
our dataset acquisition campaign (120 children, more than 45h of footage), the
children's faces were automatically detected in 98\% of the recorded frames (see
Section~\ref{sec|dataset}).
